---
title: "Lacto Summary File"
author: "Leah Boger"
date: "`r Sys.Date()`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Load Packages
```{r, message=FALSE}
library(readr)
library(agricolae)
library(ggplot2)
library(dplyr)
library(tidyverse)
library(EnvStats)
library(writexl)
library(ggbreak)
library(hrbrthemes)
```


## Lcrispatus

Load Data
```{r, message=FALSE}
lcrisp1 <- readr::read_tsv("/Users/leahboger/Desktop/Lcrispatus_ANI/4315_3209_1_ANI.tsv", col_names = FALSE)
lcrisp1ANI <- data.frame(lcrisp1)
lcrisp1ANI <- lcrisp1ANI[,3]

lcrisp3 <- readr::read_tsv("/Users/leahboger/Desktop/Lcrispatus_ANI/4313_3209_3_ANI.tsv", col_names = FALSE)
lcrisp3ANI <- data.frame(lcrisp3)
lcrisp3ANI <- lcrisp3ANI[,3]

lcrisp18 <- readr::read_tsv("/Users/leahboger/Desktop/Lcrispatus_ANI/3559_18_ANI.tsv", col_names = FALSE)
lcrisp18ANI <- data.frame(lcrisp18)
lcrisp18ANI <- lcrisp18ANI[,3]

lcrisp19 <- readr::read_tsv("/Users/leahboger/Desktop/Lcrispatus_ANI/3559_19_ANI.tsv", col_names = FALSE)
lcrisp19ANI <- data.frame(lcrisp19)
lcrisp19ANI <- lcrisp19ANI[,3]

lcrisp23 <- readr::read_tsv("/Users/leahboger/Desktop/Lcrispatus_ANI/3559_23_ANI.tsv", col_names = FALSE)
lcrisp23ANI <- data.frame(lcrisp23)
lcrisp23ANI <- lcrisp23ANI[,3]

lcrisp24 <- readr::read_tsv("/Users/leahboger/Desktop/Lcrispatus_ANI/3513_24_ANI.tsv", col_names = FALSE)
lcrisp24ANI <- data.frame(lcrisp24)
lcrisp24ANI <- lcrisp24ANI[,3]

lcrisp25 <- readr::read_tsv("/Users/leahboger/Desktop/Lcrispatus_ANI/3513_25_ANI.tsv", col_names = FALSE)
lcrisp25ANI <- data.frame(lcrisp25)
lcrisp25ANI <- lcrisp25ANI[,3]


lcrisp26 <- readr::read_tsv("/Users/leahboger/Desktop/Lcrispatus_ANI/3559_26_ANI.tsv", col_names = FALSE)
lcrisp26ANI <- data.frame(lcrisp26)
lcrisp26ANI <- lcrisp26ANI[,3]


lcrisp27 <- readr::read_tsv("/Users/leahboger/Desktop/Lcrispatus_ANI/3559_27_ANI.tsv", col_names = FALSE)
lcrisp27ANI <- data.frame(lcrisp27)
lcrisp27ANI <- lcrisp27ANI[,3]

lcrisp30 <- readr::read_tsv("/Users/leahboger/Desktop/Lcrispatus_ANI/3513_30_ANI.tsv", col_names = FALSE)
lcrisp30ANI <- data.frame(lcrisp30)
lcrisp30ANI <- lcrisp30ANI[,3]

lcrisp35 <- readr::read_tsv("/Users/leahboger/Desktop/Lcrispatus_ANI/3513_35_ANI.tsv", col_names = FALSE)
lcrisp35ANI <- data.frame(lcrisp35)
lcrisp35ANI <- lcrisp35ANI[,3]
```

Lcrispatus test for difference between strains
```{r, message=FALSE}
y <- c(lcrisp1ANI,lcrisp3ANI,lcrisp18ANI,lcrisp19ANI,lcrisp23ANI,lcrisp24ANI,lcrisp25ANI,lcrisp26ANI,lcrisp27ANI,lcrisp30ANI,lcrisp35ANI )

strain <- rep(c("lcrisp1","lcrisp3","lcrisp18","lcrisp19","lcrisp23","lcrisp24","lcrisp25","lcrisp26","lcrisp27","lcrisp30","lcrisp35"), each = 25)

l <- lm(y~strain)

#anova(l)

#check assumptions for normality and homoscedasticity
shapiro.test(l$residuals)
bartlett.test(l$resid, strain)

#Assumption of homoscedasticity and normallity not met, use nonparametric ANOVA test
kruskal.test(y~strain)
#small p-val, so appears to be significant difference between strains
```

Lcrispatus post-hoc strain variance
```{r, message=FALSE}
TukeyHSD(aov(y~strain), conf.level=0.95)
an.m<-aov(y~strain)
l<- LSD.test(an.m,"strain",p.adj = "bonferroni")
l
```



Lcrispatus kernal density
```{r}
all<-y 
boot<-sample(all,size=10000,replace = TRUE)
d<-density(boot) #kernel density estimation
df<-data.frame(boot)
df%>%
  ggplot( aes(x=boot)) +
  geom_density(fill="#69b3a2", color="#e9ecef", alpha=0.8)+
  ggtitle("Density plot of ANI value for Lcrispatus") + xlab("ANI values(bootstrapped)")
```
empirical p-value
```{r}

testANI <- read.csv("/Users/leahboger/Desktop/Lacto_ANI (1)/LC_ANI-Table 1.csv")


testANI$strain_loc1 <- paste(testANI$X, testANI$X.1)

testANI <- testANI %>% select(strain_loc1, X3513_24, X3513_25, X3513_30, X3513_35, X3559_18, X3559_19,X3559_23, X3559_26, X3559_27, X4315_3209_1, X4313_3209_3)

columns = paste(names(testANI),as.matrix(testANI[1,]))
colnames(testANI) = columns

testANI <- testANI[-1, ]
colnames(testANI)[1] ="strain_loc1"

testANI <- testANI %>% pivot_longer(-strain_loc1, names_to = "strain_loc2", values_to = "ANI")

library(EnvStats)
testANI$ANI <- as.numeric(testANI$ANI)
emp <-rep(0,nrow(testANI))
for(i in 1:nrow(testANI))
{emp[i]<-pemp(testANI$ANI[i],boot, prob.method = "emp.probs")}
t<-cbind(testANI,emp)
head(t) %>% arrange(-emp)
```


## Ljensenii

Load Data
```{r, message=FALSE}
ljensenii16 <- readr::read_tsv("/Users/leahboger/Desktop/Ljensenii_ANI/2673_16_ANI.tsv", col_names = FALSE)
ljensenii16ANI <- data.frame(ljensenii16)
ljensenii16ANI <- ljensenii16ANI[,3]

ljensenii17 <- readr::read_tsv("/Users/leahboger/Desktop/Ljensenii_ANI/2673_17_ANI.tsv", col_names = FALSE)
ljensenii17ANI <- data.frame(ljensenii17)
ljensenii17ANI <- ljensenii17ANI[,3]

ljensenii18 <- readr::read_tsv("/Users/leahboger/Desktop/Ljensenii_ANI/2673_18_ANI.tsv", col_names = FALSE)
ljensenii18ANI <- data.frame(ljensenii18)
ljensenii18ANI <- ljensenii18ANI[,3]

ljensenii19 <- readr::read_tsv("/Users/leahboger/Desktop/Ljensenii_ANI/2673_19_ANI.tsv", col_names = FALSE)
ljensenii19ANI <- data.frame(ljensenii19)
ljensenii19ANI <- ljensenii19ANI[,3]

ljensenii20 <- readr::read_tsv("/Users/leahboger/Desktop/Ljensenii_ANI/2673_20_ANI.tsv", col_names = FALSE)
ljensenii20ANI <- data.frame(ljensenii20)
ljensenii20ANI <- ljensenii20ANI[,3]

ljensenii21 <- readr::read_tsv("/Users/leahboger/Desktop/Ljensenii_ANI/2673_21_ANI.tsv", col_names = FALSE)
ljensenii21ANI <- data.frame(ljensenii21)
ljensenii21ANI <- ljensenii21ANI[,3]

ljensenii22 <- readr::read_tsv("/Users/leahboger/Desktop/Ljensenii_ANI/2673_22_ANI.tsv", col_names = FALSE)
ljensenii22ANI <- data.frame(ljensenii22)
ljensenii22ANI <- ljensenii22ANI[,3]

ljensenii23 <- readr::read_tsv("/Users/leahboger/Desktop/Ljensenii_ANI/2673_23_ANI.tsv", col_names = FALSE)
ljensenii23ANI <- data.frame(ljensenii23)
ljensenii23ANI <- ljensenii23ANI[,3]

```

Ljensenii test for difference between strain
```{r, message=FALSE}
y <- c(ljensenii16ANI, ljensenii17ANI, ljensenii18ANI, ljensenii19ANI, ljensenii20ANI, ljensenii21ANI, ljensenii22ANI, ljensenii23ANI)

strain <- rep(c("ljensenii16", "ljensenii17", "ljensenii18", "ljensenii19", "ljensenii20", "ljensenii21", "ljensenii22", "ljensenii23"), each = 25)

l <- lm(y~strain)

#anova(l)

#check assumptions for normality and homoscedasticity
shapiro.test(l$residuals)
bartlett.test(l$resid, strain)


#Assumption of homoscedasticity and normallity not met, use nonparametric ANOVA test
kruskal.test(y~strain)
#small p-val, so appears to be significant difference between strains
```


Ljensenii post-hoc strain variance
```{r, message=FALSE}
TukeyHSD(aov(y~strain), conf.level=0.95)
an.m<-aov(y~strain)
l<- LSD.test(an.m,"strain",p.adj = "bonferroni")
l
```


Ljensenii kernal density
```{r}
all<-y
boot<-sample(all,size=10000,replace = TRUE)
d<-density(boot) #kernel density estimation
df<-data.frame(boot)
df%>%
  ggplot( aes(x=boot)) +
  geom_density(fill="#69b3a2", color="#e9ecef", alpha=0.8)+
  ggtitle("Density plot of ANI value for Ljensenii") + xlab("ANI values(bootstrapped)")
```


Ljensenii empirical p
```{r}
testANI <- read.csv("/Users/leahboger/Desktop/Lacto_ANI (1)/LJ_ANI-Table 1.csv")

testANI$strain_loc1 <- paste(testANI$X, testANI$X.1)

testANI <- testANI %>% select(strain_loc1, X2673_16, X2673_17, X2673_18, X2673_19, X2673_20, X2673_21, X2673_22, X2673_23)

columns = paste(names(testANI),as.matrix(testANI[1,]))
colnames(testANI) = columns

testANI <- testANI[-1, ]
colnames(testANI)[1] ="strain_loc1"

testANI <- testANI %>% pivot_longer(-strain_loc1, names_to = "strain_loc2", values_to = "ANI")

testANI$ANI <- as.numeric(testANI$ANI)
emp<-rep(0,nrow(testANI))
for(i in 1:nrow(testANI))
{emp[i]<-pemp(testANI$ANI[i],boot,discrete = FALSE, prob.method = "emp.probs")}
t<-cbind(testANI,emp)
head(t) %>% arrange(-emp)
```



## Lparagasseri

Load data
```{r, message=FALSE}
lparagasseri4 <- readr::read_tsv("/Users/leahboger/Desktop/Lparagasseri_ANI/4892_3209_4_ANI.tsv", col_names = FALSE)
lparagasseri4ANI <- data.frame(lparagasseri4)
lparagasseri4ANI <- lparagasseri4ANI[,3]

lparagasseri6 <- readr::read_tsv("/Users/leahboger/Desktop/Lparagasseri_ANI/4933_3209_6_ANI.tsv", col_names = FALSE)
lparagasseri6ANI <- data.frame(lparagasseri6)
lparagasseri6ANI <- lparagasseri6ANI[,3]

lparagasseri7 <- readr::read_tsv("/Users/leahboger/Desktop/Lparagasseri_ANI/4898_3209_7_ANI.tsv", col_names = FALSE)
lparagasseri7ANI <- data.frame(lparagasseri7)
lparagasseri7ANI <- lparagasseri7ANI[,3]

lparagasseri15 <- readr::read_tsv("/Users/leahboger/Desktop/Lparagasseri_ANI/3559_15_ANI.tsv", col_names = FALSE)
lparagasseri15ANI <- data.frame(lparagasseri15)
lparagasseri15ANI <- lparagasseri15ANI[,3]

lparagasseri17 <- readr::read_tsv("/Users/leahboger/Desktop/Lparagasseri_ANI/3559_17_ANI.tsv", col_names = FALSE)
lparagasseri17ANI <- data.frame(lparagasseri17)
lparagasseri17ANI <- lparagasseri17ANI[,3]

lparagasseri23 <- readr::read_tsv("/Users/leahboger/Desktop/Lparagasseri_ANI/3513_23_ANI.tsv", col_names = FALSE)
lparagasseri23ANI <- data.frame(lparagasseri23)
lparagasseri23ANI <- lparagasseri23ANI[,3]

lparagasseri27 <- readr::read_tsv("/Users/leahboger/Desktop/Lparagasseri_ANI/3513_27_ANI.tsv", col_names = FALSE)
lparagasseri27ANI <- data.frame(lparagasseri27)
lparagasseri27ANI <- lparagasseri27ANI[,3]

lparagasseri28 <- readr::read_tsv("/Users/leahboger/Desktop/Lparagasseri_ANI/3513_28_ANI.tsv", col_names = FALSE)
lparagasseri28ANI <- data.frame(lparagasseri28)
lparagasseri28ANI <- lparagasseri28ANI[,3]


lparagasseri3513_31 <- readr::read_tsv("/Users/leahboger/Desktop/Lparagasseri_ANI/3513_31_ANI.tsv", col_names = FALSE)
lparagasseri3513_31ANI <- data.frame(lparagasseri3513_31)
lparagasseri3513_31ANI <- lparagasseri3513_31ANI[,3]

lparagasseri3559_31 <- readr::read_tsv("/Users/leahboger/Desktop/Lparagasseri_ANI/3559_31_ANI.tsv", col_names = FALSE)
lparagasseri3559_31ANI <- data.frame(lparagasseri3559_31)
lparagasseri3559_31ANI <- lparagasseri3559_31ANI[,3]


lparagasseri32 <- readr::read_tsv("/Users/leahboger/Desktop/Lparagasseri_ANI/3513_32_ANI.tsv", col_names = FALSE)
lparagasseri32ANI <- data.frame(lparagasseri32)
lparagasseri32ANI <- lparagasseri32ANI[,3]

lparagasseri33 <- readr::read_tsv("/Users/leahboger/Desktop/Lparagasseri_ANI/3513_33_ANI.tsv", col_names = FALSE)
lparagasseri33ANI <- data.frame(lparagasseri33)
lparagasseri33ANI <- lparagasseri33ANI[,3]

lparagasseri34 <- readr::read_tsv("/Users/leahboger/Desktop/Lparagasseri_ANI/3513_34_ANI.tsv", col_names = FALSE)
lparagasseri34ANI <- data.frame(lparagasseri34)
lparagasseri34ANI <- lparagasseri34ANI[,3]


lparagasseri50 <- readr::read_tsv("/Users/leahboger/Desktop/Lparagasseri_ANI/3329_50_ANI.tsv", col_names = FALSE)
lparagasseri50ANI <- data.frame(lparagasseri50)
lparagasseri50ANI <- lparagasseri50ANI[,3]

lparagasseri51 <- readr::read_tsv("/Users/leahboger/Desktop/Lparagasseri_ANI/3329_51_ANI.tsv", col_names = FALSE)
lparagasseri51ANI <- data.frame(lparagasseri51)
lparagasseri51ANI <- lparagasseri51ANI[,3]

lparagasseri52 <- readr::read_tsv("/Users/leahboger/Desktop/Lparagasseri_ANI/3329_52_ANI.tsv", col_names = FALSE)
lparagasseri52ANI <- data.frame(lparagasseri52)
lparagasseri52ANI <- lparagasseri52ANI[,3]

lparagasseri55 <- readr::read_tsv("/Users/leahboger/Desktop/Lparagasseri_ANI/3329_55_ANI.tsv", col_names = FALSE)
lparagasseri55ANI <- data.frame(lparagasseri55)
lparagasseri55ANI <- lparagasseri55ANI[,3]

lparagasseri57 <- readr::read_tsv("/Users/leahboger/Desktop/Lparagasseri_ANI/3329_57_ANI.tsv", col_names = FALSE)
lparagasseri57ANI <- data.frame(lparagasseri57)
lparagasseri57ANI <- lparagasseri57ANI[,3]
```



Lparagasseri test for difference between strain
```{r, message=FALSE}
y <- c(lparagasseri4ANI, lparagasseri6ANI, lparagasseri7ANI, lparagasseri15ANI, lparagasseri17ANI, lparagasseri23ANI, lparagasseri27ANI, lparagasseri28ANI, lparagasseri3513_31ANI, lparagasseri3559_31ANI, lparagasseri32ANI, lparagasseri33ANI, lparagasseri34ANI, lparagasseri50ANI, lparagasseri51ANI, lparagasseri52ANI, lparagasseri55ANI, lparagasseri57ANI)

strain <- rep(c("lparagasseri4", "lparagasseri6", "lparagasseri7", "lparagasseri15", "lparagasseri17", "lparagasseri23", "lparagasseri27", "lparagasseri28", "lparagasseri3513_31", "lparagasseri3559_31", "lparagasseri32", "lparagasseri33", "lparagasseri34", "lparagasseri50", "lparagasseri51", "lparagasseri52","lparagasseri55", "lparagasseri57"), each = 25)

l <- lm(y~strain)

#anova(l)

#Check assumptions of homoskedacisity and normality
shapiro.test(l$residuals)
bartlett.test(l$resid, strain)


#Assumptions are not met,use nonparametric ANOVA
kruskal.test(y~strain)
#small p-val, so appears to be significant difference between strains

```

Lparagasseri post-hoc strain variance
```{r, message=FALSE}
TukeyHSD(aov(y~strain), conf.level=0.95)
an.m<-aov(y~strain)
l<- LSD.test(an.m,"strain",p.adj = "bonferroni")
l
```


Lparagasseri kernal density
```{r}
all<-y
boot<-sample(all,size=10000,replace = TRUE)
d<-density(boot) #kernel density estimation
df<-data.frame(boot)
df%>%
  ggplot( aes(x=boot)) +
  geom_density(fill="#69b3a2", color="#e9ecef", alpha=0.8)+
  ggtitle("Density plot of ANI value for Lparagasseri") + xlab("ANI values(bootstrapped)")
```

Lparagasseri empirical p
```{r}
testANI <- read.csv("/Users/leahboger/Desktop/Lacto_ANI (1)/LP_ANI-Table 1.csv")

testANI$strain_loc1 <- paste(testANI$X, testANI$X.1)

testANI <- testANI %>% select(strain_loc1, X3329_50, X3329_51, X3329_52, X3329_55, X3329_57, X3513_23, X3513_27, X3513_28, X3513_31, X3513_32, X3513_33, X3513_34, X3559_15, X3559_17, X3559_31, X4892_3209_4, X4898_3209_7, X4933_3209_6)

columns = paste(names(testANI),as.matrix(testANI[1,]))
colnames(testANI) = columns

testANI <- testANI[-1, ]
colnames(testANI)[1] ="strain_loc1"

testANI <- testANI %>% pivot_longer(-strain_loc1, names_to = "strain_loc2", values_to = "ANI")

testANI$ANI <- as.numeric(testANI$ANI)
emp<-rep(0,nrow(testANI))
for(i in 1:nrow(testANI))
  {emp[i]<-pemp(testANI$ANI[i],boot, prob.method = "emp.probs")}
t<-cbind(testANI,emp)
head(t) %>% arrange(-emp)
```


## Liners

Load data
```{r, message=FALSE}
liners24 <- readr::read_tsv("/Users/leahboger/Desktop/Liners_ANI/3559_24_ANI.tsv", col_names = FALSE)
liners24ANI <- data.frame(liners24)
liners24ANI <- liners24ANI[,3]

liners25 <- readr::read_tsv("/Users/leahboger/Desktop/Liners_ANI/3559_25_ANI.tsv", col_names = FALSE)
liners25ANI <- data.frame(liners25)
liners25ANI <- liners25ANI[,3]

liners28 <- readr::read_tsv("/Users/leahboger/Desktop/Liners_ANI/3559_28_ANI.tsv", col_names = FALSE)
liners28ANI <- data.frame(liners28)
liners28ANI <- liners28ANI[,3]

liners29 <- readr::read_tsv("/Users/leahboger/Desktop/Liners_ANI/3559_29_ANI.tsv", col_names = FALSE)
liners29ANI <- data.frame(liners29)
liners29ANI <- liners29ANI[,3]

liners30 <- readr::read_tsv("/Users/leahboger/Desktop/Liners_ANI/3559_30_ANI.tsv", col_names = FALSE)
liners30ANI <- data.frame(liners30)
liners30ANI <- liners30ANI[,3]
```



Liners test for difference between strain
```{r, message=FALSE}
y <- c(liners24ANI, liners25ANI, liners28ANI,liners29ANI, liners30ANI)

strain <- rep(c("liners24", "liners25", "liners28", "liners29", "liners30"), each = 25)

l <- lm(y~strain)

#anova(l)

#Check assupmtions of homokedascity and normality
shapiro.test(l$residuals)
bartlett.test(l$resid, strain)


#Assumptions are not met, use nonparametric ANOVA
kruskal.test(y~strain)
#small p-val, so appears to be significant difference between strains
```


Liners post-hoc strain variance
```{r, message=FALSE}
TukeyHSD(aov(y~strain), conf.level=0.95)
an.m<-aov(y~strain)
l<- LSD.test(an.m,"strain",p.adj = "bonferroni")
l
```


Liners kernal density
```{r}
all<-y
boot<-sample(all,size=10000,replace = TRUE)
d<-density(boot) #kernel density estimation
df<-data.frame(boot)
df%>%
  ggplot( aes(x=boot)) +
  geom_density(fill="#69b3a2", color="#e9ecef", alpha=0.8)+
  ggtitle("Density plot of ANI value for Liners") + xlab("ANI values(bootstrapped)")
```

Liners empirical p
```{r}
testANI <- read.csv("/Users/leahboger/Desktop/Lacto_ANI (1)/LI_ANI-Table 1.csv")

testANI$strain_loc1 <- paste(testANI$X, testANI$X.1)

testANI <- testANI %>% select(strain_loc1, X3559_24, X3559_25, X3559_28, X3559_29, X3559_30)

columns = paste(names(testANI),as.matrix(testANI[1,]))
colnames(testANI) = columns

testANI <- testANI[-1, ]
colnames(testANI)[1] ="strain_loc1"

testANI <- testANI %>% pivot_longer(-strain_loc1, names_to = "strain_loc2", values_to = "ANI")

testANI$ANI <- as.numeric(testANI$ANI)
emp<-rep(0,nrow(testANI))
for(i in 1:nrow(testANI))
{emp[i]<-pemp(testANI$ANI[i],boot, prob.method = "emp.probs")}
t<-cbind(testANI,emp)
head(t) %>% arrange(-emp)
```


## Lgasseri

load data
```{r, message=FALSE}
lgasseri10 <- readr::read_tsv("/Users/leahboger/Desktop/Lgasseri_ANI/3559_10_ANI.tsv", col_names = FALSE)
lgasseri10ANI <- data.frame(lgasseri10)
lgasseri10ANI <- lgasseri10ANI[,3]

lgasseri53 <- readr::read_tsv("/Users/leahboger/Desktop/Lgasseri_ANI/3329_53_ANI.tsv", col_names = FALSE)
lgasseri53ANI <- data.frame(lgasseri53)
lgasseri53ANI <- lgasseri53ANI[,3]

lgasseri54 <- readr::read_tsv("/Users/leahboger/Desktop/Lgasseri_ANI/3329_54_ANI.tsv", col_names = FALSE)
lgasseri54ANI <- data.frame(lgasseri54)
lgasseri54ANI <- lgasseri54ANI[,3]

lgasseri56 <- readr::read_tsv("/Users/leahboger/Desktop/Lgasseri_ANI/3329_56_ANI.tsv", col_names = FALSE)
lgasseri56ANI <- data.frame(lgasseri56)
lgasseri56ANI <- lgasseri56ANI[,3]

```



Lgasseri test for difference between strain
```{r, message=FALSE}
y <- c(lgasseri10ANI, lgasseri53ANI, lgasseri54ANI, lgasseri56ANI)

strain <- rep(c("lgasseri10", "lgasseri53", "lgasseri54", "lgasseri56"), each = 25)

l <- lm(y~strain)

#anova(l)

#check assumptions of normality and homoskadaticity
shapiro.test(l$residuals)
bartlett.test(l$resid, strain)


#Assumptions not met, use nonparametric ANOVA
kruskal.test(y~strain)
#small p-val, so appears to be significant difference between strains
```


Lgasseri post-hoc strain variance
```{r, message=FALSE}
TukeyHSD(aov(y~strain), conf.level=0.95)
an.m<-aov(y~strain)
l<- LSD.test(an.m,"strain",p.adj = "bonferroni")
l
```


Lgasseri kernal density
```{r}
all<-y
boot<-sample(all,size=10000,replace = TRUE)
d<-density(boot) #kernel density estimation
df<-data.frame(boot)
df%>%
  ggplot( aes(x=boot)) +
  geom_density(fill="#69b3a2", color="#e9ecef", alpha=0.8)+
  ggtitle("Density plot of ANI value for Lgasseri") + xlab("ANI values(bootstrapped)")
```


Lgasseri empirical p
```{r}
testANI <- read.csv("/Users/leahboger/Desktop/Lacto_ANI (1)/LG_ANI-Table 1.csv")

testANI$strain_loc1 <- paste(testANI$X, testANI$X.1)

testANI <- testANI %>% select(strain_loc1, X3329_53, X3329_54, X3329_56, X3513_21, X3559_10, X3559_9)

columns = paste(names(testANI),as.matrix(testANI[1,]))
colnames(testANI) = columns

testANI <- testANI[-1, ]
colnames(testANI)[1] ="strain_loc1"

testANI <- testANI %>% pivot_longer(-strain_loc1, names_to = "strain_loc2", values_to = "ANI")

testANI$ANI <- as.numeric(testANI$ANI)
emp<-rep(0,nrow(testANI))
for(i in 1:nrow(testANI))
{emp[i]<-pemp(testANI$ANI[i],boot, prob.method = "emp.probs")}
t<-cbind(testANI,emp)
head(t) %>% arrange(-emp)
```
